### 2022-06-29 manuscript/manuscript.Rmd
replace the use of the term m/z peaks with m/z signals

As the amu width of spectral binning decreased, there was an exponential increase in the number of spectral features observed along with an increase in the proportion of missing values across all the example biological matrices (Supplementary Tables S2 & S3).
This was a result of the measured deviation in *m/z* peaks both between each scan of a sample and between samples.
The peak at 133.01416 *m/z* from the *B. distachyon* leaf matrix was found to deviate by a range of up to  `r format(scan_deviation, scientific = FALSE) %>% as.character()` amu between the infusion scans of a single injection and `r format(sample_deviation,scientific = FALSE) %>% as.character()` amu across the 10 injections (Supplementary Figure S3). 
These deviations are due changes in parameters such as temperature and space charge compensation during the Fourier transformation, which is calculated on a scan by scan basis [@hu2005]. 
This means that *m/z* have the potential to freely shift between bins at widths of 0.0001 or less and so contribute to the high proportions of missing data. 
Due to this, the use of bin widths of 0.0001 amu and below would be unsuitable for spectral binning.

@@

The accuracy of some of the extracted accurate m/z peaks from the chemical standards mix are shown in Table \@ref(tab:accurate-masses).
A full list of the matched accurate *m/z* can be found in Supplementary Table S4. 
Out of a total of `r nrow(standards_adduct_mzs)` predicted ionisation products based on the selected common adducts, `r unique_matches` (`r signif(unique_matches/nrow(standards_adduct_mzs) * 100,digits = 3)`%) were matched to accurate *m/z* that had been assigned to 0.01 amu bins.
These matches had an average ppm error of `r ppm_error$Mean` (SE = $\pm$ `r ppm_error$SE`) with `r below_3_ppm` (`r prop_below_3_ppm`%) having an error below 3 ppm.
This level of accuracy obtained across the majority of detected features is sufficient to allow for the assignment of putative molecular formulas or metabolite annotations [@kind2006]

>>>>

As the amu width of spectral binning decreased, there was an exponential increase in the number of spectral features observed along with an increase in the proportion of missing values across all the example biological matrices (Supplementary Tables S2 & S3).
This was a result of the measured deviation in *m/z* signals both between each scan of a sample and between samples.
The peak at 133.01416 *m/z* from the *B. distachyon* leaf matrix was found to deviate by a range of up to  `r format(scan_deviation, scientific = FALSE) %>% as.character()` amu between the infusion scans of a single injection and `r format(sample_deviation,scientific = FALSE) %>% as.character()` amu across the 10 injections (Supplementary Figure S3). 
These deviations are due changes in parameters such as temperature and space charge compensation during the Fourier transformation, which is calculated on a scan by scan basis [@hu2005]. 
This means that *m/z* have the potential to freely shift between bins at widths of 0.0001 or less and so contribute to the high proportions of missing data. 
Due to this, the use of bin widths of 0.0001 amu and below would be unsuitable for spectral binning.

@@

The accuracy of some of the extracted accurate *m/z* signals from the chemical standards mix are shown in Table \@ref(tab:accurate-masses).
A full list of the matched accurate *m/z* can be found in Supplementary Table S4. 
Out of a total of `r nrow(standards_adduct_mzs)` predicted ionisation products based on the selected common adducts, `r unique_matches` (`r signif(unique_matches/nrow(standards_adduct_mzs) * 100,digits = 3)`%) were matched to accurate *m/z* that had been assigned to 0.01 amu bins.
These matches had an average ppm error of `r ppm_error$Mean` (SE = $\pm$ `r ppm_error$SE`) with `r below_3_ppm` (`r prop_below_3_ppm`%) having an error below 3 ppm.
This level of accuracy obtained across the majority of detected features is sufficient to allow for the assignment of putative molecular formulas or metabolite annotations [@kind2006]
